---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# walmartAPI

[![Travis build status](https://travis-ci.org/EmilHvitfeldt/walmartAPI.svg?branch=master)](https://travis-ci.org/EmilHvitfeldt/walmartAPI) [![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/walmartAPI)](https://cran.r-project.org/package=walmartAPI)
![downloads](http://cranlogs.r-pkg.org/badges/grand-total/walmartAPI)

The goal of **walmartAPI** is to give access to the API created by [walmartlabs](https://developer.walmartlabs.com/) to search products, locate stores etc etc.

To use this package you will need an API key which you can acquire by signing up on this website https://developer.walmartlabs.com/member.

## Installation

**walmartAPI** is available on CRAN and can be installed normally with 

```{r cran-installation, eval = FALSE}
install.packages("walmartAPI") #from CRAN 
``` 
or you can install **walmartAPI** from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("EmilHvitfeldt/walmartAPI")
```

## Examples

This package provides a handful for functionalities. We are able to look up a specific product based on an ID.

```{r, eval=FALSE}
library(tidyverse)
library(walmartAPI)

key <- "************************"

walmartAPI::lookup(id = 19336123, key = key)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(walmartAPI)
walmartAPI::lookup(id = 19336123, key = "z2gz6g9jefqsjsye7fttakey")
```

search in products using plain text

```{r, eval=FALSE}
walmartAPI::searching("ipod", key = key)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
walmartAPI::searching("ipod", key = "z2gz6g9jefqsjsye7fttakey")
```

and locate stores in your area

```{r, eval=FALSE}
store_locator(city = "Houston", key = key)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
store_locator(city = "Houston", key = "z2gz6g9jefqsjsye7fttakey")
```
